The one characterizing the parental care stages

### 2019-10-11 docs/ms1-charactization.Rmd
typos

### Fig 1: graphical abstract of methods

@@

## Fig 2: hormones

@@

## Figure 3: general rnaseq pattern, tissue > sex > stage

_Needs to be replaced with a better PCA plot_

@@

## Figure 4: model showing ability to predict non-parental, egg care, and nestingling care

@@

## Figure 5: PRL in prolatin mirrors PRL in bloo

@@

## Figure 6: many genes mirror the PRL expression pattern

@@

## Data availabilty

>>>>

### Fig 1: Graphical abstract of methods

@@

## Fig 2: Prolactin fluctuates the most and peaks near hatch in males and females

@@

## Figure 3: General RNAseq pattern, tissue > sex > parental stage

_Needs to be replaced with a better PCA plot showing all samples as points_

@@

## Figure 4: model showing ability to predict non-parental, egg care, and nestling care

_redo color scheme, fix titles_

@@

## Figure 5: PRL gene expression in the pituitary in prolactin mirrors PRL in blood

@@

## Figure 6: Many genes mirror the PRL expression pattern

@@

## Data availability
